External priors for the next generation of CMB experiments.

### 2015-12-11 Notes/CMBS4_priors_paper_.tex
add legit DiValentino ref
journal version

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_snow_mass_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{
Constraints on the sum of the neutrino masses as a function of priors on cosmological parameters. 
Each prior is expressed in units of the error that would be obtained internally from the CMB S4 experiment (+Planck+current BAO); e.g., $\sigma(H_0)_{\rm S4 + Planck Pol + BAO15}=0.6\%$, so the value of unity on the x-axis corresponds to imposing an external prior on $H_0$ of 0.6\%.
The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI. The bottom-most curve shows the impact of imposing the given prior on {\it all} the other parameters simultaneously.
$H_{0}$ and $\Omega_{c}h^{2}$ are shown to be the most important external priors to improve neutrino mass constraints. We chose a fiducial value $\sum m_{\nu}=85 $ meV.}
\label{fig:prior_omeganuh2}
\end{center}
\end{figure}
%==========

@@

\reffig{prior_omeganuh2} shows the projected errors on $\sum m_\nu$ from CMB-S4 (+Planck+current BAO) as a function of external priors. 
Without any external priors (far right in figure), upcoming CMB experiments are poised to obtain 1-sigma limits on $\sum m_\nu$ of order 25 meV, corresponding to a 2-sigma detection even in the worst case scenario. Adding in external priors helps this significantly though, as discussed, for example, in \cite{2013arXiv1309.5383A,pan:2015a,allison:2015}. 
There, the added prior was ``DESI BAO'', representing a measurement of distances as a function of redshift from the baryon acoustic oscillation feature probed by DESI. This is represented by the blue band in \reffig{prior_omeganuh2}. In addition to showing the implications of introducing this fixed external constraint, \reffig{prior_omeganuh2} generalizes the extent to which external information will improve the neutrino mass constraints. For example, the red curve shows the improvement as additional information on the Hubble constant is applied. The projected, marginalized constraint on $H_0$ from just CMB-S4+Planck+BAO15 is $0.6\%$ (and similarly the values for the other parameters are given below the figure). So imposing {\it external} information with this value of $\sigma_{H_0}/H_0=0.006$ corresponds to 1 on the $x$-axis. This would improve the neutrino mass constraint to 17 meV. Similarly, introducing an external constraint on the dark matter density equal to its internal constraint of 0.4\% (so again 1 on the $x$-axis) improves the projected neutrino mass constraint to 20 meV. It is not surprising that this is close to the constraint obtained with DESI because the BAO distances in this model depends most sensitively on $\Omega_ch^2$ and $H_{0}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_omnuh2_snow_mass_lmin=50_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Same as \reffig{prior_omeganuh2} but with $\ell^{\rm CMB-S4}_{\rm min}>50$. Here $A_{s}$ and $\tau$ priors will also helps because of their degeneracy with $\sum m_{\nu}$.}

@@

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_massless_neutrinos_snow_mass_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Projected 1-sigma error on $N_{\rm eff}$ as a function of external priors. The parameters that would be most useful to constrain externally for the purposes of determining $N_{\rm eff}$ are $n_s$ and $\Omega_bh^2$.}
\label{fig:prior_massless_neutrinos}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{prior_w_snow_mass_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Constraints on the dark energy equation of state $w$ as a function of external priors on cosmological parameters. 
An external prior on $H_{0}$ will be crucial to improve the constraint.} 
\label{fig:prior_w}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{{ellipse_H0_w_snow_mass_lmin=4_lmax=4499_ndet=1000000_fsky=0.75}.pdf}
\caption{Two dimensional constraint (CMB S4 + Planck) 1$\sigma$ ellipse for $w,H_{0}$ space. The dashed (red) line correspond to values in the plane corresponding to the same distance to the last scattering surface.} 
\label{fig:ellipse_w_H0}
\end{center}
\end{figure}
%==========

>>>>

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_omnuh2.pdf}
\caption{
Constraints on the sum of the neutrino masses as a function of priors on cosmological parameters. 
Each prior is expressed in units of the error that would be obtained internally from the CMB S4 experiment (+Planck+current BAO); e.g., $\sigma(H_0)_{\rm S4 + Planck Pol + BAO15}=0.6\%$, so the value of unity on the x-axis corresponds to imposing an external prior on $H_0$ of 0.6\%.
The horizontal (blue) line correspond to CMB S4 experiment + Planck Pol + DESI. The bottom-most curve shows the impact of imposing the given prior on {\it all} the other parameters simultaneously.
$H_{0}$ and $\Omega_{c}h^{2}$ are shown to be the most important external priors to improve neutrino mass constraints. We chose a fiducial value $\sum m_{\nu}=85 $ meV.}
\label{fig:prior_omeganuh2}
\end{center}
\end{figure}
%==========

@@

\reffig{prior_omeganuh2} shows the projected errors on $\sum m_\nu$ from CMB-S4 (+Planck+current BAO) as a function of external priors. 
Without any external priors (far right in figure), upcoming CMB experiments are poised to obtain 1-sigma limits on $\sum m_\nu$ of order 25 meV, corresponding to a 2-sigma detection even in the worst case scenario. Adding in external priors helps this significantly though, as discussed, for example, in \cite{di-valentino:2015,2013arXiv1309.5383A,pan:2015a,allison:2015}. 
There, the added prior was ``DESI BAO'', representing a measurement of distances as a function of redshift from the baryon acoustic oscillation feature probed by DESI. This is represented by the blue band in \reffig{prior_omeganuh2}. In addition to showing the implications of introducing this fixed external constraint, \reffig{prior_omeganuh2} generalizes the extent to which external information will improve the neutrino mass constraints. For example, the red curve shows the improvement as additional information on the Hubble constant is applied. The projected, marginalized constraint on $H_0$ from just CMB-S4+Planck+BAO15 is $0.6\%$ (and similarly the values for the other parameters are given below the figure). So imposing {\it external} information with this value of $\sigma_{H_0}/H_0=0.006$ corresponds to 1 on the $x$-axis. This would improve the neutrino mass constraint to 17 meV. Similarly, introducing an external constraint on the dark matter density equal to its internal constraint of 0.4\% (so again 1 on the $x$-axis) improves the projected neutrino mass constraint to 20 meV. It is not surprising that this is close to the constraint obtained with DESI because the BAO distances in this model depends most sensitively on $\Omega_ch^2$ and $H_{0}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_omnuh2_50.pdf}
\caption{Same as \reffig{prior_omeganuh2} but with $\ell^{\rm CMB-S4}_{\rm min}>50$. Here $A_{s}$ and $\tau$ priors will also helps because of their degeneracy with $\sum m_{\nu}$.}

@@

%==========
\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_massless_neutrinos.pdf}
\caption{Projected 1-sigma error on $N_{\rm eff}$ as a function of external priors. The parameters that would be most useful to constrain externally for the purposes of determining $N_{\rm eff}$ are $n_s$ and $\Omega_bh^2$.}
\label{fig:prior_massless_neutrinos}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{prior_w.pdf}
\caption{Constraints on the dark energy equation of state $w$ as a function of external priors on cosmological parameters. 
An external prior on $H_{0}$ will be crucial to improve the constraint.} 
\label{fig:prior_w}
\end{center}
\end{figure}
%==========

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{ellipse_H0_w.pdf}
\caption{Two dimensional constraint (CMB S4 + Planck) 1$\sigma$ ellipse for $w,H_{0}$ space. The dashed (red) line correspond to values in the plane corresponding to the same distance to the last scattering surface.} 
\label{fig:ellipse_w_H0}
\end{center}
\end{figure}
%==========
